Comparing Generative Pre-trained Transformer Models to Physicians for Assigning Causes of Death from Verbal Autopsy: A Case Study of 6939 Deaths in Sierra Leone from 2019-2022

### 2024-07-06 manuscript/manuscript.tex
Working on conclusion

@@

The datasets supporting the conclusions of this article are included within the article (and its additional files).

>>>>

\subsection*{Funding}

TBD.

\subsection*{Competing interests}

Not applicable.

\subsection*{Ethics approval}

TBD.

\subsection*{Consent for publication}

Not applicable.

@@

The datasets supporting the conclusions of this article are included within the article (and its additional files) and on \url{https://openmortality.org}.

\subsection*{Code availability}

The R and Python code is available on \url{https://github.com/cghr-toronto/rapid-paper1}.

\subsection*{Authors' contributions}

PJ and PB are the study Principal Investigators. ATA and RK implemented the data collection procedures. RW, CC, LN, and TKSN processed, documented, and prepared the data. RW, ASL, and RK ran the models. RW wrote the paper and conducted the analysis. AB provided medical domain guidance and feedback. All authors reviewed the results and contributed to the report. All authors read and approved the final manuscript.
